THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@

The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective operators like -
\frac{1}{3}(\phi^{\dagger}\phi)^3 and \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) to calculate 
the deviation of Higgs boson-fermion couplings from SM. In the effective beyond standard model theory, there are dimension 5 and 
dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon 
minus lepton number symmetry conservation processes.

>>>>

The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators like \frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and 
(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM. The first operator shift the minimum of the Higgs potential. Also as there is a rescaling of the Higgs field due to the introduction of these operators in the potential term, Higgs-Fermion couplings are modified. In the effective beyond standard model theory, there are dimension 5 and dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.

@@
